Using Semantic Similarity to Assist Assessing MCR Comment Usefulness

### 2014-07-26 sections/approach.tex
Edited up though Case Study section
Added a title! We need to rearrange and remove some sections :( I’ll
work on it during my long trim ride to Tokyo on Sunday

\section{Reviewers' Comments Classification Approach}
\begin{figure}[!t]
\centering
\includegraphics[scale=0.35, trim = 50 90 0 30, clip=true]{overview2}
\caption{Overview of our classification approach.}
\label{fig:overview}
\end{figure}

Fig. \ref{fig:overview} shows the overview of our proposed approach.
We classified the usefulness of comments by measuring similarity between commit message of proposed change and its comments.
To calculate similarity in Fig. \ref{fig:overview}(a), we used Vector Space Model (VSM) which is a well-known technique for retrieving similar documents written in unstructured natural language.
Euclidian distance is also used to calculate dissimilarity.
For our training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The overview figure does not have (a) and (b)...}
The results from Fig. \ref{fig:overview}(a) and from Fig. \ref{fig:overview}(b) are then used to estimate the similarity and dissimilarity threshold that can best discriminate useful/useless comments. Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history.

To classify usefulness of comment using similarity and dissimilarity, we first formalize our classification model as follows:
\begin{itemize}
\item \textbf{useful}: $\Theta(c,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
\item \textbf{useless}: $\Omega(c,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
\end{itemize}
where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; and $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification.

The functions $\Sim(m,c)$ and $\Dist(m,c)$ represents the similarity and dissimilarity of the text of the comment $c$, compared to the corresponding change's commit message $m$.
Two metrics are used because they are independently generated and thus provides more dimensions for classification.
We also found experimentally that using two metrics gives better performance than just one.

The details our approach is described in the following subsections.

\subsection{Similarity and Dissimilarity Calculation based on VSM}
%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language. In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
To do so, we use VSM which is a model for representing text documents as vectors.
For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
The $w_{t,d}$ value is tf-idf weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $\operatorname{tf}_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.

@@

\subsection{Estimating Similarity and Dissimilarity Threshold}
We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that can maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$. This is an accuracy measurement for a binary classification considering an accuracy of prediction (precision) and  a coverage of classification (recall). This can be calculated using Equation \ref{eq:fmeasure}.

\begin{equation}
\begin{split}
\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
\\
\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
\\
\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
\end{split}
\label{eq:fmeasure}
\end{equation}

Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ as predict model to identify useful comments , $\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} and are actually useful; $\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} but are actually useless; and $\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model predict as \textit{useless} but are actually useful. To measuring F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ model, it uses the same consideration but change the determination to useless comments. For the correctness of prediction, we determine from the useful/useless defined dataset.

>>>>

\section{Semantic Similarity Classification of Comment Usefulness}
\begin{figure}[!t]
\centering
\includegraphics[scale=0.34, trim = 50 90 0 30, clip=true]{overview2}
\caption{Overview of our classification approach.}
\label{fig:overview}
\end{figure}

Our goal is to improve the efficiency and confidence in determining the usefulness of review comments. As discussed previously, this is largely based on relevance the comment has to the proposed change (as documented within a MCR system). According to relevance theory, a primary factor in relevance is similarly, and so it is natural for us to consider classification \emph{similarity conditions}. 
\dan{can we find a reference for relevance and similarly?}
That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful. Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity} , the less relevant, and hence less useful. Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification. That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely not useful. The key is determining these degrees in a practical and effective manner. While this representation is straightforward and automatically adjusts ti the quality of the data, it has a few drawbacks. First, we have to accept that some comments cannot be reliably or confidently classified. We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} i.e. unable to assess (subjectively) comment usefulness. Again, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets. This decreases the cost-effectiveness limiting the practicality of application to projects with a large enough number of comments whee the classification effort saved overcomes the training costs.  
% empirically driven and automatically adapts to the quality the data
 Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
Usefulness of a comment is determined by computing its semantic similarity with the commit message of proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}. The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives. In our case example we chose to maximize the F-measure, but other likelihood functions could be used depending on precision, recall, or risk goals.    
To calculate semantic similarity Fig. \ref{fig:overview}(a), we used the Vector Space Model (VSM) with the cosine distance measure which is a well-known technique for retrieving similar documents written in unstructured natural language. 
The Euclidian distance is a well-established measure of dissimilarity and applies analogously.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}
The training data is a small set of randomly-selected pairs of comments and corresponding commit messages are manually assessed for usefulness. For statistical purposes at least 30 useful and 30 useless comments are needed. The similarity and dissimilarities are computed for the data set. These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history according to the classification model as follows:
\begin{itemize}
\item \textbf{useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
\item \textbf{useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
\item \textbf{undetermined}: Neither of the above conditions are $\True$.
\end{itemize}

The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$.
Two metrics are used because they are independently generated and thus provides better discrimination for classification.
We also found experimentally that using two metrics has higher performance than just one.

The details of our approach are elaborated in the following subsections.

\dan{**** ALERT **** this entire subsection is not needed! Everything in it is well-known and can simply be referenced. I suggest removing it if we need the space.  I have not edited this section .... }
\subsection{Similarity and Dissimilarity Calculation based on VSM}
%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language. In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
To do so, we use VSM which is a model for representing text documents as vectors.
For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
The $w_{t,d}$ value is tf-idf weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $\operatorname{tf}_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.

@@

\subsection{Estimating Similarity and Dissimilarity Thresholds}
Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ to classify useful comments and we have the following values:

$\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} and are \textit{actually useful} i.e. true-positives;

$\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} but are \textit{actually useless} i.e. false positives;

$\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model classifies as \textit{useless} but are \textit{actually useful}.

We can now define the following classification  performance measures: 
\begin{equation}
\begin{split}
\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
\\
\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
\\
\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
\end{split}
\label{eq:fmeasure}
\end{equation}

We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$ Equation \ref{eq:fmeasure}. This is a performance measurement for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).

The F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ is computed analogously where we change instances of useful to useless and vice-versa in the definitions. The correctness of classification is determined from the useful/useless defined dataset.

### 2014-07-26 sections/background.tex
Edited up though Case Study section
Added a title! We need to rearrange and remove some sections :( I’ll
work on it during my long trim ride to Tokyo on Sunday

%\section{Background}
%In this section, we describe MCR process based on Gerrit system. Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques. 
\section{Modern Code Review Process}

An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}. The grey area shows the review process of the system which composed of four main steps. (1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system. (2) reviewers examine the proposed code changes whether it contains defects or not. (3) reviewers will give comments where should the author improve the code change. The author will create a new change according to the comments then re-submit a new patch again. Then, reviewers will examine the new change. If there is still a needed improvement, reviewers will give comments to fix again. The steps (1)-(3) will be iterated until reviewers can determine that this changes can be merge to the project or should not be merge (reject the change).

According to this process, reviewers' comment is the most important for the software quality. McIntosh et. al. \cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs. However, as tool supporting MCR allows reviewers freely write a message to the author, it is often seen that some comments are not clearly identify defects and ineffective. Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper in design\cite{Bacchelli2013a}. Our observation in Qt project also correspond this finding. We found some comments are superficial and unrelated to the proposed changes. For example, a superficial and unconfident reviewer as shown in Fig. \ref{fig:example}(a), a comment for rule of using Version Control System (e.g. Git) in the project Fig. \ref{fig:example}(b).

>>>>

%\section{Background}
%In this section, we describe MCR process based on Gerrit system. Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques. 
\dan{this section seems to only cover MCR. We could have this be a Background section with this and the other subsequent sections moved to sub-sections}
\section{Modern Code Review Process}

An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}. The grey area shows the review process of the system which composed of four main steps. (1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system. (2) reviewers examine the proposed code changes for defects or concerns. (3) reviewers provide comments to the author. The author creates a revised proposed change according to the comments then re-submits for review. Then, reviewers will examine the revised proposed change. If the revision is not approved, reviewers provide comments to fix and the process continues until reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).

According to this process, reviewers' comments are the most important factor in determining software quality. In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs. However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers) and frequently comments are superficial or do not clearly identify defects or relevant issues (e.g. design suggestions, coding styles, etc.) for the proposed change and are thus of questionable usefulness. For example a comment may relate to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. "Keep up the good work!"). Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues. Our observations of the Qt project also correspond to this finding. We found some comments are superficial and unhelpful to the proposed changes. For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information. While the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

### 2014-07-26 sections/introduction.tex
Edited up though Case Study section
Added a title! We need to rearrange and remove some sections :( I’ll
work on it during my long trim ride to Tokyo on Sunday

Because performance of code review has a clear relationship to the quality of software project, many studies have investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}. However, little research exists investigating how the discussion for a proposed change impacts software quality. Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it is possible that reviewers comments can either positively contribute to the proposed changes (i.e. "useful"), or be a discussion which is out of scope (i.e. "useless" relative to the proposed changes). Not surprisingly the amount of useless comments appears to increase with project size. Yet notably so too does the ratio of useless to useful comments. 
%\dan{Do you think we can find a reference for this?}
This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR. Current research has focused mostly on the relation between number of comments and quality. To the best of our knowledge the connection between degree of useful and useless comments and quality has not been studied. One reason for this may be that to assess the impact of discussion in MCR, a manual classification is required as in the study of Beller et. al. \cite{Beller}. MCR can produce a massive amount of changes and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify the comments to perform appropriate quantitative analysis. Moreover, unlike a checklist in used formal inspection, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.  Fig. \ref{fig:example} show typical MCR comments illustrating these issues.  
%\pick{Need some connection. Says that Massive amount of commits and comment it would be expensive to manually identify. It's natural language }
\begin{figure}[!t]
\centering
\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
\caption{An simplified version of MCR Process based on Gerrit system}
\label{fig:process}
\end{figure}

%\dan{Much of the following material should be placed in a separate Motivation section} 
In this paper we present a text mining approach to assisting in classifying the usefulness of comments. The purposed approach is meant to enable classifying the large amounts of MRC comments needed to conduct comment and code quality studies such as those discussed earlier. Manual classification can quickly become an untenable task. Our modest OSS case study has a over 17,000 potentially useful comments. At an optimistic 5 seconds peer comment classification we would expect about 24 person-hours of effort. Furthermore manual classification is subjective and error-prone. By introducing some automation support based on objective empirical criteria, the method we propose here aims to both reduce effort and increase confidence in classification to a degree practical for addressing very large MRC data sets. Because usefulness of a comment is not precisely defined and a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.

@@

For our case study of the method, we use a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation. For training and validation of our approach, three experts manually classified the usefulness for 320 comments. We also apply our predictive model to the full set of 
17,000 
%\dan{what's the actual number?}
comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:

\noindent \textbf{RQ1:} Is VSM similarity a good indicator of MRC comment usefulness?\\
\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
\noindent \textbf{RQ3:} Is VSM similarity classification cost-efficient, assurable, and scalable?
%\dan{******** HERE *******}
\noindent The main contributions of this paper are:
\begin{itemize}
\item We propose an approach to mine natural text of comments in code reviews and classify their usefulness.
\item The experimental results show that our approach can classify comments with an F$_1$ score of 0.681 and 0.693.
\item We found that 85\% of comments in Gerrit are automatically generated. In the remaining 15\%, about 43\% of them are classified as useful, while about 34\% are classified as not useful comments. The remaining 23\% cannot be clearly classified.
\end{itemize} 
%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.

>>>>

Because performance of code review has a clear relationship to the quality of software project, many studies have investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}. However, little research exists investigating how the discussion for a proposed change impacts software quality. Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it is possible that reviewers comments can either positively contribute to the proposed changes (i.e. "useful"), or be a discussion which is out of scope (i.e. "useless" relative to the proposed changes). Not surprisingly the amount of useless comments appears to increase with project size. Yet notably so too does the ratio of useless to useful comments. 
\dan{Do you think we can find a reference for this?}
This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR. Current research has focused mostly on the relation between number of comments and quality. To the best of our knowledge the connection between degree of useful and useless comments and quality has not been studied. One reason for this may be that to assess the impact of discussion in MCR, a manual classification is required as in the study of Beller et. al. \cite{Beller}. MCR can produce a massive amount of changes and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify the comments to perform appropriate quantitative analysis. Moreover, unlike a checklist in used formal inspection, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.  Fig. \ref{fig:example} show typical MCR comments illustrating these issues.  
%\pick{Need some connection. Says that Massive amount of commits and comment it would be expensive to manually identify. It's natural language }
\begin{figure}[!t]
\centering
\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
\caption{An simplified version of MCR Process based on Gerrit system}
\label{fig:process}
\end{figure}

\dan{Much of the following material should be placed in a separate Motivation section} 
In this paper we present a text mining approach to assisting in classifying the usefulness of comments. The purposed approach is meant to enable classifying the large amounts of MRC comments needed to conduct comment and code quality studies such as those discussed earlier. Manual classification can quickly become an untenable task. Our modest OSS case study has a over 17,000 potentially useful comments. At an optimistic 5 seconds peer comment classification we would expect about 24 person-hours of effort. Furthermore manual classification is subjective and error-prone. By introducing some automation support based on objective empirical criteria, the method we propose here aims to both reduce effort and increase confidence in classification to a degree practical for addressing very large MRC data sets. Because usefulness of a comment is not precisely defined and a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.

@@

For our case study of the method, we use a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation. For training and validation of our approach, three experts manually classified the usefulness for 320 comments. We also apply our predictive model to the full set of 
17,000 
\dan{what's the actual number?}
comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:

\noindent \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?\\
\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
\noindent \textbf{RQ3:} Is semantic similarity classification cost-efficient, assurable, and scalable?

\noindent In addition to addressing the research questions above, the main contributions of this paper are:
\dan{these are more "results" than contributions.... need to reword this!}
\begin{itemize}
\item A practical to apply approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
\item The experimental results show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping). For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful. The remaining 23\% are undetermined and require manual classification. Thus the classification effort is reduced by about 77\%.
\item xx\% of the comments did not have unanimity (i.e. unclear), and of these yy\% were automatically determined to be useful or not useful. Follow up with dissenting assessors found mis-judgement occurred zz\% of the time whereby in retrospect the comment would have had unanimity. This indicates the method is useful in identifying subjective judgement errors. 
\item Of the 23\% not automatically classified (i.e. undetermined), qq\% were unclear. Of the (1-qq)\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear. This indicates the method is useful in identifying chance unanimity errors or group think bias.
\end{itemize} 
%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.

### 2014-07-26 sections/methods.tex
Edited up though Case Study section
Added a title! We need to rearrange and remove some sections :( I’ll
work on it during my long trim ride to Tokyo on Sunday

\section{Case Study Design}

We used the review history of Qt project from Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of small subsystems. For our case study, we selected the most active subproject \texttt{qtbase} project. From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.

@@

\subsection{Data Preparation}
We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we firstly processed the commit message and comments as follows:

\subsubsection{Automatically generated messages removal}
In Gerrit, the comments are composed of comment messages from reviewers and automated messages. These automatic messages are generated by Gerrit and integration system to record activities, for example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}. Since these messages are not impact to software quality\cite{Mcintosh}, we removed them from our data set. We identified these automatic messages using regular expression and selecting frequently appeared pattern of messages.

@@

\subsubsection{Data Preprocessing}
 we extracted semantic words commit messages and comment messages before converting to vector. For each message, we removed all punctuation signs, digits, and common words (e.g. a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}. We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.

@@

\subsubsection{Ground-Truth Data Preparation}
To prepare ground-truth data, we read comments and manually identified useful and useless comments. In this study, we use three people (the first two authors and one student) independently classify comments by giving a question that ``Does this comment technically contribute to its change or not?''. Then, the readers gave a vote for \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless. From the voting scores, we regarded that the comments with three \texttt{YES} votes are \textbf{useful} comments and the comments with no \texttt{YES} votes (i.e. three \texttt{NO} votes) are \textbf{useless} comments. For the comments with one and two \texttt{YES}' votes, we remained them as \textbf{unclear} comments which we cannot confidently defined.

@@

\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}\\
\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection. Then, we used these comments for both training and test data set for our approach to determine an effectiveness of our approach. We also determined the robustness of our approach using cross validation. We randomly selected 90\% of 320 comments for training set and 10\% for test set.
The effectiveness was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times and find average of accuracy.

>>>>

\section{Case Study}

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject \texttt{qtbase} project. From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.

@@

\subsection{Data Preparation}
We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we first processed the commit message and comments as follows:

\subsubsection{Automatically generated messages removal}
In Gerrit, the comments are composed of comment messages from reviewers and automated messages. These automatic messages are generated by Gerrit and the integration system to record activities. For example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}. Since these messages are generally recored keeping, they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition. In practice they are not considered in code review. They are easily determined as useless by our method and would artificially improve our classification performance. We identified these automatic messages using regular expressions and selecting frequently appeared patterns of messages.

@@

\subsubsection{Data Preprocessing}
 As is customary for VSM processing we extracted semantic words from commit messages and comment messages before converting to vector. For each message, we removed all punctuation signs, digits, and common words (e.g. a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}. We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.

@@

\subsubsection{Ground-Truth Data Preparation}
To prepare ground-truth data, a team of three experienced developers independently read comments and manually assessed them useful or useless. The assessors were asked to answer for each comment the question ``Does this comment technically contribute to its proposed change?''. Then, the assessors cast their vote as \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless.  Comments with three \texttt{YES} votes are classified as \textbf{useful} comments and comments with three \texttt{NO} votes are \textbf{useless}. Comments lacking unanimity (i.e. one or two \texttt{YES} votes are deemed \textbf{unclear} and without confident usefulness.

@@

\noindent \textbf{RQ1: Is semantic similarity a good indicator of MCR comment usefulness?}\\
\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection. Then, we used these comments for both the training and test data set for our approach to determine its effectiveness. We also determined the robustness of our approach using cross validation. We randomly selected 90\% of 320 comments for training set and 10\% for test set.
The effectiveness was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times and find average of accuracy.

\dan{What what the effort in person-hours for this?}
